Draft

### 2017-06-29 Thesis/Draft.tex
Scripts for calibrating algorithms

The idea now is that we would like to classify the banners into two
distinct groups: A group with a mean conversion rate \(\mu_i\) below
threshold \(\tau\), and a group with mean conversion rate \(\mu_i\)
above threshold \(\tau\). This might be the optimization problem when we
are concerned with not falling below a certain minimum level
click-through rate with the banners we're choosing.

@@

In any case, the problem boils down to the following. As standard in
multi-armed bandit problems, we have \(K\) arms
\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
collect feedback in form of the random variable \(X_{k,t}\) which is
distributed accoring to the arm's distribution \(\nu_k\). In general, we
are concerned with estimating for each arm \(i\) the mean \(\mu_i\) of
its distribution \(\nu_i\). In contrast to most bandit problems,
however, we do not directly compare arms with each other by comparing
their means. In the case of pure exploration bandits, it is for example
necessary to compare the arms because one aims to find the best one. In
the case of the thresholding bandit, however, we compare each arm's mean
\(\mu_i\) individually against the threshold \(\tau \in \mathbb{R}\)
which is known and fixed before the experiment. One might compare this
to a pure exploration bandit in which the mean of the best arm is known
upfront. We will see later that this fact leads to advantages in the
design of algorithms which are not as readily available in other bandit
settings.

In Locatelli (2016), the arms' distributions are assumed to follow a
\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
able to proof a general lower bound as well as an algorithm with a
matching upper bound. Both hinge upon the \emph{complexity} of a given
problem. Since bandit problems can differ in the number of the arms
\(K\) and the means of each arm, some pose easier identification
problems than others. Indeed, in the thresholding problem, the
difficulty of the problem naturally depends on how close (the means of
the) distributions are to the fixed threshold. Intuitively, the closer a
mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it will
be to distinguish the two successfully based on samples from the
distribution \(\nu_i\). For the case of the sub-Gaussian distributions,
a natural measure of this distance is given by simply
\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
ourselves to make a mistake at no cost.

If we extend this idea to the set of arms \(i \in \{1,...,K\}\) of a
given bandit problem, a natural measure of the overall diffulty of the
problem, or the problem's complexity, might be given by
\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
adding additional arms leads to an increase in complexity (since we need
to sample more of them), just as smaller \(\Delta_i\) will increase the
complexity as arms become harder to classify. (WHERE DOES THIS
COMPLEXITY ORIGINALLY COME FROM? WHAT IS ITs MOTIVATION? ITS NOT THAAAT
NATURAL)

@@

Another characteristic uniquely identifying bandit problems is the
regret measure that we aim to optimize. As explained during the
introduction, multi-armed bandits traditionally optimize cumulative
regret. The notion of regret considered in the thresholding bandit,
however, is more akin to the regret in pure exploration bandits or the
error probability in sequential hypothesis testing. Indeed, one can most
easily describe the regret in the thresholding case as the probability
of making a misclassification of any arm. Or, more rigorously, let us
define the set of all arms with mean larger than the threshold,
\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
Consequently,
\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
of the sampling rule/procedure (!!we have not mentioned yet the fact
that we're in the fixed budget case!!), we demand that any algorithm
returns the two corresponding \emph{estimated} sets:
\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
as well as
\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
We simply demand an answer to the question which arms have means above
the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
the overall number of samples the algorithm is allowed to pull. We
define the loss as
\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
That is, we compare the return set with the true set and collect a loss
of 1 if any arm with a true mean outside the \(2\epsilon\) interval
around \(\tau\) was misclassified. It is important to realize that arms
with means inside the \(2 \epsilon\) interval may be misclassified
without it affecting the loss. These arms are considered close enough to
the threshold that we do not care whether they lie above or below.

@@

From the general setup, we already know how the algorithm will end.
After it has drawn \(T\) samples, the algorithm makes its decision of
which arms to include in the return sets solely on basis of the
empirical means \(\hat{\mu}_i(T)\) estimated until time \(T\).
Furthermore, the threshold and interval around the threshold were fixed
upfront and serve as argument to the algorithm: \((\tau, \epsilon)\).
For a given arm \(i\) and a given time \(t\), we let \(T_i(t)\)
represent the number of samples drawn from arm \(i\) until time \(t\)
(including). Consequently, the empirical mean of arm \(i\) at time \(t\)
is given by \(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\)
where \(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\)
when the arm is pulled for the \(s\)-th time.

@@

\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
often with corresponding mean close to the threshold and interval (small
\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
on arms which appear to be inherently difficult to classify based on the
samples collected until time \(T_i(t)\), as these arms stifle the
confidence the most. That is, until we have collected enough evidence to
make a confident classification even if the mean is truly close to the
threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
Consequently, other arms farther away from the threshold will be sampled
again. In this way, the algorithm tries to distribute the budget \(T\)
over all arms so as to define a sampling rule optimizing the confidence
of the final decision. Of course, that's just Glivenko-Cantelli and the
CLT making sure \(B_i(t+1)\) is not degenerate.

@@

Where the APT algorithm shows room for improvement is when it comes to
settings with distributions that are not sub-Gaussian. This is mentioned
in Locatelli et al. (2016). In general, the problem becomes that the
assumptions for the bounds no longer hold; furthermore, the statistic
\(B_i(t+1)\), and the term \(\hat{\Delta_i}(t)\) are motivated by
(sub-)Gaussian distributions. The more one moves away from Gaussian-like
distributions, the less appropriate this term becomes, however. In
particular, the empirical mean will be less concentrated around the true
mean and more impacted by outliers which are more likely under non
sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
Bubeck et al. (2013) which considers solutions for multi-armed bandits
that are based on heavy-tail distributions. By using more robust
estimators of the mean, one could equip the APT algorithm to deal with
such distributions.

Another step towards dealing with non sub-Gaussianity is made by
Mukherjee et al. (2017) who use an estimate of the variance additionally
to the empirical mean in their Augmented UCB solution. Utilizing this
additional information, the algorithm seems to perform better than for
example APT, going from simulation results displayed in the paper. We
will continue to discuss the Augmented UCB solution further in chapter
3.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show
bounds based on the Kullback-Leibler divergence of the specific
distribution directly. While the approximation through the Gaussian
Kullback-Leibler divergence in the lower bound proof is convenient and
leads to the simple APT algorithm, it might not stay appropriate for
distributions whose Kullback-Leibler divergence tends to differ from the
Gaussian. This, for example, is the case for Bernoulli distributions at
very small parameters \(\mu\). It's quite obvious simply by looking at
examples that the Kullback-Leibler divergence of Bernoullis starts to
lose any similarity to the plain quadratic approximation. The second
graph then shows, that the actual Kullback-Leibler divergence of
Bernoullis also has lost any symmetry over this range of parameter
values. Given that Bernoulli distributions with very small parameter
values arise naturally in many applications in website optimization and
advertising click-through modeling, there is a need to tackle this
problem.

@@

\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
1 of Locatelli et al. (2016), a lower bound for the thresholding bandit
problem is shown. The basic idea is as follows. The problem formulation
considered in the paper describes bandit problems for sub-Gaussian
distributions. To show a lower bound, we show that every algorithm is
expected to make a certain error even if we restrict ourselves to a very
restricted scenario. Even then, any algorithm will have a certain level
of risk with which it cannot distinguish between the actual setting and
slightly changed settings (under which the former answer leads to
regret).

@@

\paragraph{Reminder about the goal of the
proof}\label{reminder-about-the-goal-of-the-proof}

@@

\paragraph{Statistical Decision}\label{statistical-decision}

@@

\paragraph{Change of Distribution}\label{change-of-distribution}

@@

\paragraph{Concentration of the Empirical Kullback-Leibler
Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}

@@

\paragraph{\texorpdfstring{Bounding \(T_i\) for
\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}

@@

\paragraph{Bringing everything
together}\label{bringing-everything-together}

@@

The Hoeffding inequality as used here is as follows:

@@

\paragraph{Step 2: Lower Bound on Number of Pulls of Difficult
Arm}\label{step-2-lower-bound-on-number-of-pulls-of-difficult-arm}

@@

\paragraph{Step 3: Lower Bound on Number of Pulls of Simple
Arm}\label{step-3-lower-bound-on-number-of-pulls-of-simple-arm}

@@

\paragraph{Conclusion}\label{conclusion}

@@

Even though the complexity \(H\) enjoys popularity in the literature of
the best m arm identification problem, \(m \geq 1\), Kaufmann et al.
(2016) show explicitly that \(H\) is mainly useful for problems of
Gaussian distributions. Indeed, they go so far as to define new measures
of complexity that are based on information theoretic metrics. Using
those they then display \(H\) as an approximation to their measures in
the case of Gaussian distributions. In turn, this makes apparent that
especially Bernoulli distributions with small means have to be treated
differently.

@@

To proof this statement, we assume as before that the arms are ordered
by their means decreasing in size. For a given \(\delta\)-PAC algorithm
\(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
conditions, there exists for every arm \(a \in \{1, \dots, K\}\) an
alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, only arm \(a\) is modified in accordance with
the continuity conditions. Modified in such a way that measured by the
Kullback-Leibler divergence, the arm \(\nu_{m+1}\) is now closer to
\(\nu_a\) than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
(consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
\(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away from \(\nu_a\)
just enough so that \(\nu_a\) is closer to \(\nu_m\) than to \(\nu_a'\)
(consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
the original set of optimal arms, \(\{1,\dots,m\}\) no longer optimal
under the alternative model \(\nu'\). Given that the algorithm returns
\(\hat{S}_m\), we know that for the event
\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
by the stopping time \(\tau\) induced \(\sigma\)-Algebra
\(\mathcal{F}_{\tau}\)), that
\(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!).

@@

\paragraph{Matching algorithm
strategies}\label{matching-algorithm-strategies}

Given those lower bounds, all that is left is to find algorithms which
are able to match the complexity. Sadly, not straightforward for
Bernoullis.

@@

A very similar application of the KL divergence has been given in
Garivier and Kaufmann to derive a lower bound on the sample complexity
in the case of best arm identification. In particular, the
transportation Lemma 1 is used again. And a matching algorithm for
\(K \geq 2\) arms is proposed.

@@

>>>>

The idea now is that we would like to classify the banners into two
distinct groups: A group with mean conversion rates \(\mu_i\) below
threshold \(\tau\), and a group with mean conversion rates \(\mu_i\)
above threshold \(\tau\). This might be the optimization problem when we
are concerned with not falling below a certain minimum level
click-through rate with the banners we're choosing.

@@

In any case, the problem boils down to the following. As standard in
multi-armed bandit problems, we have \(K\) arms
\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
collect feedback in form of the random variable \(X_{k,t}\) which is
distributed according to the arm's distribution \(\nu_k\). In general,
we are concerned with estimating for each arm \(i\) the mean \(\mu_i\)
of its distribution \(\nu_i\). In contrast to most bandit problems,
however, we do not directly compare arms with each other by comparing
their means. That would for example be the case for pure exploration
bandits, where it is necessary to compare the arms because one aims to
find the best one relative to the others. In the case of the
thresholding bandit, however, we compare each arm's mean \(\mu_i\)
individually against the threshold \(\tau \in \mathbb{R}\) which is
known and fixed before the experiment. One might compare this to a pure
exploration bandit in which the mean of the best arm is known upfront.
We will see later that this fact leads to advantages in the design of
algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an
\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
able to proof a general lower bound as well as an algorithm with a
matching upper bound. Both hinge upon the \emph{complexity} of a given
problem. Since bandit problems can differ in the number of the arms
\(K\) and the means of each arm, some pose easier identification
problems than others. Indeed, in the thresholding problem, the
difficulty of the problem naturally depends on how close (the means of
the) distributions are to the fixed threshold. Intuitively, the closer a
mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it will
be to distinguish the two successfully based on samples from the
distribution \(\nu_i\). For the case of the sub-Gaussian distributions,
a natural measure of this distance is given by simply
\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
ourselves to make a mistake at no cost.

If we extend this idea to the set of arms \(i \in \{1,...,K\}\) of a
given bandit problem, a natural measure of the overall diffulty of the
problem, or the problem's complexity, might be given by
\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
adding additional arms leads to an increase in complexity (since we need
to sample more of them), just as smaller \(\Delta_i\) will increase the
complexity as arms become harder to classify. (WHERE DOES THIS
COMPLEXITY ORIGINALLY COME FROM?)

@@

Another characteristic uniquely identifying bandit problems is the
regret measure that we aim to optimize. As explained during the
introduction, multi-armed bandits traditionally optimize cumulative
regret. The notion of regret considered in the thresholding bandit,
however, is more akin to the simple regret in pure exploration bandits
or the error probability in sequential hypothesis testing. Indeed, one
can most easily describe the regret in the thresholding case as the
probability of making a misclassification of any arm. Or, more
rigorously, let us define the set of all arms with mean larger than the
threshold,
\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
Consequently,
\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
of the sampling rule/procedure (!!we have not mentioned yet the fact
that we're in the fixed budget case!!), we demand that any algorithm
returns the two corresponding \emph{estimated} sets:
\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
as well as
\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
We simply demand an answer to the question which arms have means above
the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
the overall number of samples the algorithm is allowed to pull. We
define the loss as
\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
That is, we compare the return set with the true set and collect a loss
of 1 if any arm with a true mean outside the \(2\epsilon\) interval
around \(\tau\) was misclassified. It is important to realize that arms
with means inside the \(2 \epsilon\) interval may be misclassified
without it affecting the loss. These arms are considered close enough to
the threshold that we do not care whether they lie above or below.

@@

From the general setup, we already know how the algorithm will end.
After it has drawn \(T\) samples, the algorithm makes its decision of
which arms to include in the return sets solely on basis of the
empirical means \(\hat{\mu}_i(T)\) estimated based on the samples drawn
until time \(T\). Furthermore, the threshold and interval around the
threshold were fixed upfront and serve as argument to the algorithm:
\((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
let \(T_i(t)\) represent the number of samples drawn from arm \(i\)
until time \(t\) (including). Consequently, the empirical mean of arm
\(i\) at time \(t\) is given by
\(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
arm is pulled for the \(s\)-th time.

@@

\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
often with corresponding mean close to the threshold and interval (small
\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
on arms which appear to be inherently difficult to classify based on the
samples collected until time \(T_i(t)\), as these arms stifle the
confidence the most. That is, until we have collected enough evidence to
make a confident classification even if the mean is truly close to the
threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
Consequently, other arms farther away from the threshold will be sampled
again. In this way, the algorithm tries to distribute the budget \(T\)
over all arms so as to define a sampling rule optimizing the confidence
of the final decision. This is Glivenko-Cantelli and the CLT making sure
\(B_i(t+1)\) is not degenerate. (?)

@@

Where the APT algorithm shows room for improvement is when it comes to
settings with distributions that are not sub-Gaussian. This is mentioned
in Locatelli et al. (2016). In general, the problem becomes that the
assumptions for the bounds no longer hold; furthermore, the statistic
\(B_i(t+1)\), and the term \(\hat{\Delta}_i(t)\) are motivated by
(sub-)Gaussian distributions. The more one moves away from Gaussian-like
distributions, the less appropriate this term becomes, however. In
particular, the empirical mean will be less concentrated around the true
mean and more impacted by outliers which are more likely under non
sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
Bubeck et al. (2013) which considers solutions for multi-armed bandits
that are based on heavy-tail distributions. By using more robust
estimators of the mean, one could equip the APT algorithm to deal with
such distributions.

Another step towards dealing with non sub-Gaussianity is made by
Mukherjee et al. (2017) who use an estimate of the variance additionally
to the empirical mean in their Augmented UCB solution. Utilizing this
additional information, the algorithm seems to perform better than for
example APT, going from simulation results displayed in the paper.
However, the simulations deal exclusively with normal distributions, as
the variance has to be bounded for the upper bound of the Augmented UCB
to hold. We will continue to discuss the Augmented UCB solution in
chapter 3.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show
bounds based on the Kullback-Leibler divergence of the specific
distribution directly. While the approximation through the Gaussian
Kullback-Leibler divergence in the lower bound proof is convenient and
leads to the simple APT algorithm, it might not stay appropriate for
distributions whose Kullback-Leibler divergence tends to differ from the
Gaussian. This, for example, is the case for Bernoulli distributions at
very small parameters \(\mu\). By looking at the graphical examples
below it becomes obvious that the Kullback-Leibler divergence of
Bernoullis starts to lose any similarity to the plain quadratic
approximation. The second graph then shows that the actual
Kullback-Leibler divergence of Bernoullis also has lost any symmetry
over this range of parameter values. Given that Bernoulli distributions
with very small parameter values arise naturally in many applications in
website optimization and advertising click-through modeling, there is a
need to tackle this problem.

@@

\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
\ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower
bound for the thresholding bandit problem is shown. The basic idea is as
follows. The problem formulation considered in the paper describes
bandit problems for sub-Gaussian distributions. To show a lower bound,
we show that every algorithm is expected to make a certain error even if
we restrict ourselves to a very restricted scenario. Even then, any
algorithm will have a certain level of risk with which it cannot
distinguish between the actual setting and slightly changed settings
(under which the former answer leads to regret).

@@

\subsubsection{Reminder about the goal of the
proof}\label{reminder-about-the-goal-of-the-proof}

@@

\subsubsection{Statistical Decision}\label{statistical-decision}

@@

\subsubsection{Change of Distribution}\label{change-of-distribution}

@@

\subsubsection{Concentration of the Empirical Kullback-Leibler
Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}

@@

\subsubsection{\texorpdfstring{Bounding \(T_i\) for
\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}

@@

\subsubsection{Bringing everything
together}\label{bringing-everything-together}

@@

The Hoeffding inequality as used here is as follows (compare chapter 2.4
in \href{http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf}{David
Pollard (2015)}):

@@

\subsubsection{Step 2: Lower Bound on Number of Pulls of Difficult
Arm}\label{step-2-lower-bound-on-number-of-pulls-of-difficult-arm}

@@

\subsubsection{Step 3: Lower Bound on Number of Pulls of Simple
Arm}\label{step-3-lower-bound-on-number-of-pulls-of-simple-arm}

@@

\subsubsection{Conclusion}\label{conclusion}

@@

Even though the complexity \(H\) enjoys popularity in the literature of
the best \(m\) arm identification problem, \(m \geq 1\), Kaufmann et al.
(2016) show explicitly that \(H\) is mainly useful for problems of
Gaussian distributions. Indeed, they go so far as to define new measures
of complexity that are based on information theoretic measures Using
those they then display \(H\) as an approximation to their measures in
the case of Gaussian distributions. In turn, this makes apparent that
especially Bernoulli distributions with small means have to be treated
differently.

@@

To proof this statement, we assume as before that the arms are ordered
by their means decreasing in size. For a given \(\delta\)-PAC algorithm
\(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
conditions (compare Kaufmann et al. (2016)), there exists for every arm
\(a \in \{1, \dots, K\}\) an alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, only arm \(a\) is modified in accordance with
the continuity conditions. Modified in such a way that measured by the
Kullback-Leibler divergence, the arm \(\nu_{m+1}\) is now closer to
\(\nu_a\) than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
(consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
\(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away from \(\nu_a\)
just enough so that \(\nu_a\) is closer to \(\nu_m\) than to \(\nu_a'\)
(consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
the original set of optimal arms, \(\{1,\dots,m\}\) no longer optimal
under the alternative model \(\nu'\). Given that the algorithm returns
\(\hat{S}_m\), we know that for the event
\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
by the stopping time \(\tau\) induced \(\sigma\)-Algebra
\(\mathcal{F}_{\tau}\)), that
\(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!).

@@

\subsubsection{Matching algorithm
strategies}\label{matching-algorithm-strategies}

Given these lower bounds, all that is left is to find algorithms which
are able to match the complexity. Sadly, not straightforward for
Bernoullis.

@@

A very similar application of the KL divergence has been given in
Garivier and Kaufmann (2016) to derive a lower bound on the sample
complexity in the case of best arm identification. In particular, the
transportation Lemma 1 is used again. And a matching algorithm for
\(K \geq 2\) arms is proposed.

@@

\section{KL and Bayesian Thresholding
Bandits}\label{kl-and-bayesian-thresholding-bandits}

\subsection{Introduction}\label{introduction}

We have introduced the thresholding bandit problem in chapter 1. The APT
algorith described in Locatelli et al. (2016) is able to match a lower
bound (be more specific!) given in the same paper, and has several
favorable characteristics such as its overall simplicity and it being an
anytime algorithm. However, the bounds on the expected loss assume the
arms' distributions to be \(R\)-sub-Gaussian. This is reflected in the
algorithm's complexity measure
\(H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}\), where
\(\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon\), which -- given
the known threshold \(\tau \pm \epsilon\) -- only depends on the
distribution's mean. This is appropriate for Gaussian arms with equal
variances, but potentially inefficient for other kinds of distributions.

In the case of Gaussian distributions with varying variances, for
example, it makes sense to take the variance into account; after all,
given two Gaussians with equal mean, intuitively we would prefer to get
a sample from the distribution of larger variance.

In the case of Gaussians, the complexity \(H\) is nice also because it
reflects the Kullback-Leibler divergence between two Gaussians. And
since Bernoulli distributions are bounded on the interval \([0,1]\),
they are consequently sub-Gaussian, meaning that their Kullback-Leibler
divergence can be approximated by the Gaussian one. However, while
Bernoullis are sub-Gaussian, the approximation of their divergence by
the Gaussian divergence becomes less and less optimal as the parameter
(and thus mean) goes to \(0\) or \(1\), as shown in chapter 1. And while
online advertisements might not be an obvious use case for thresholding
bandits, they are just one real life scenario dominated by Bernoulli
distributions with very small parameters. Thus it is worthwile to adapt
current solutions of the thresholding bandit problem to cases in which
the Gaussian Kullback-Leibler divergence is no longer an appropriate
approximation.

Large motiviation for the idea of adjusting the complexity measure (and
thus the algorithms) to distributions more generally based on the
Kullback-Leibler divergence stems from the work discussed in chapter 2,
complexity measures were defined for the pure exploration bandits in
terms of the Kullback-Leibler divergence. Based on this, the authors
were for example able to point our differences between Gaussian and
Bernoulli bandits. We expect that results in a similar vain could be
derived for thresholding bandits.

To this end, in the following, we first present an extension of mean
based algorithms to an algorithm that incorporates empirical variances
as described in Mukherjee et al. (2017). Afterwards, we propose and
discuss potential further improvements based on Kullback-Leibler
divergence and Bayesian posterior distributions. Finally, we compare the
performance of different algorithms based on simulations and real world
data sets.

\subsection{Variance Based Algorithms for Thresholding
Bandits}\label{variance-based-algorithms-for-thresholding-bandits}

Mukherjee et al. (2017) propose an algorithm based on variance estimates
called Augmented-UCB (AugUCB). The setting in which the algorithm is
proposed is very similar to the setting in Locatelli et al. (2016). The
algorithm itself, however, differs heavily from the APT algorithm. So is
AugUCB for example not an anytime algorithm. Furthermore, arms can be
deleted in every round if there are ``far enough'' away from the mean.
Both the decision of which arm is played in a given round, and whether
an arm is removed from the active set of arm, is based not only on the
empirical mean estimate \(\mu_i(t)\), but also on a term \(s_i\) that is
increasing linearly in the estimated standard deviation. While the APT
algorithm plays the arm minimizing the quantity
\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
AugUCB plays the arm minimizing the quantity
\((\hat{\Delta}_i(t) - 2s_i)\), where \(s_i\) is based on the variance
estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
\(T\), and an elimination parameter \(\rho\) (compare Algorithm 1 in
Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
\end{equation*}

Consequently, the authors also introduce complexity measures which take
the variance into account. From Gabillon et al. (2011) they use
\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
Furthermore, with
\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
and with \(\stackrel{\sim}{\Delta}_{(i)}\) being an increasing ordering
of \(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the
AugUCB algorithm's expected loss, it could be replaced by
\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
\(H_{\sigma,1}\) is of course more directly comparable to the complexity
\(H\) that we are used to.

While in the case of the APT algorithm the number of times a specific
arm has been drawn \(T_i\) measures how concentrated the estimated mean
is around the true mean (and thus for large \(T_i\) an arm is no longer
drawn even if \(\hat{\mu}\) is close to \(\tau\)); in the case of the
AugUCB algorithm this is regulated by the combination of the variance
estimate \(\hat{v}_i\) and the exploration factor \(\psi_m\), where they
ensure that certain arms are no longer pulled when the algorithm is
sufficiently confident in its knowledge about the true mean. Therefore,
when using a very similar favorable event in the proof of their upper
bound, Mukherjee et al. (2017) have to bound the probability that an an
arm is not removed from the active set after the a certain number of
rounds -- even though the arm is above (respectively below) the
threshold. If this probability is low, then this means that the
algorithm is able to be certain about an arm's true mean \emph{quickly}
by employing variance estimates. In comparison, Locatelli et al (2016)
used bounds on on how often arms are drawn (\(T_i\)) to give a bound on
the probability of the favorable event. In order to derive the bound,
Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the
distributions have rewards bounded in \([0,1]\) in order to derive the
bound on the probability that an arm has not been eliminated correctly
in round \(T_i\). Thus, the distributions for which their upper bound
holds are a subset of the sub-Gaussian distributions considered in
Locatelli et al. (2016). However, it is not that the authors need to
assume that the rewards are in \([0,1]\), but this was assumed so that
the variance of the distribution is in \([0,1]\). Thus, the upper bound
holds in particular for Gaussian distributions with variance
\(\sigma^2 \in [0,1]\).

Based on this assumption, the authors show that the probability that an
arm has not been eliminated after \(m_i\) rounds is given by (compare
equation (2) in Mukherjee et al., 2017):

\begin{equation} \label{Mukherjee2017Equation2}
\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
\end{equation}

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
that the left part of the RHS gives the probability that the mean
estimate is out of wack, while the right term gives the probability that
the variance is overestimated. The first term is bounded by the
Bernstein inequality. In the cumulative regret setting, there exists a
similar decomposition that bounds the expected number of pulls of a
suboptimal arm. Compare for example chapter 3.1 in ``Thompson Sampling:
An Asymptotically Optimal Finite Time Analysis'' by Kaufmann, Korda and
Munos (2012). There they decompose the expected number of draws of an
suboptimal arm for an optimistic (UCB like) into the probability that
the optimal arm's mean is underestimated, and the probability that the
UCB of the suboptimal arm is still very large. To give bounds for UCB
algorithms, it is then shown that these two terms show a certain
convergence. Mukherjee et al. do similarly for their variance based
algorithm in the thresholding setting.

(since the AugUCB eliminates arms, it is interesting to see how it
behaves when the underlying CTR changes over time\ldots{})

\subsection{New Approaches}\label{new-approaches}
